%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\renewcommand{\labelitemi}{$\bullet$}

\name{Ian Gallagher} % Your name

%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(831)818-9080 \\ iangallagherm@gmail.com} % Your phone number and email
\address{www.linkedin.com/in/ianmichaelgallagher}
\address{6249 Gushee Street, Felton, CA} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf California Polytechnic State University, San Luis Obispo} \hfill {August 2017 - Present} 
\\ Bachelor of Science, \textbf{Mathematics}, expected June 2021 \hfill {GPA: \textbf{3.9}}
%\\ Concentration: \textbfd{Applied Mathematics}
\\ Minor: \textbf{Computer Science}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Software Team Member}{November 2019 - Present}{Cal Poly CubeSat Laboratory}{}
\item Worked on CubeSat flight software for various lab missions.
\item Software designed for Linux platforms. Programming primarily in C and Python.
\item Lab made use of revision control systems, including git, gitlab, and svn.
\item Software lead for NASA ER-2 payload designed to record in-flight vibrational profile.
\end{rSubsection}

\begin{rSubsection}{Frost Research Scholar}{June 2019 - September 2019}{Cal Poly Mathematics Department}{}
\item Researched the underlying mathematical properties of low order glacial climate models.
\item Investigated the interactions between internal free oscillations and external forcing signals, focusing on changes in model behavior over a range of parameter regimes.
\item Model and analysis code written in Matlab.
\end{rSubsection}

\begin{rSubsection}{Frost Research Scholar}{June 2020 - September 2020}{Cal Poly Mathematics Department}{}
\item Part of a team of three undergraduate students investigating the structure of the maximal tori of the generalized quaternions.
\item Work was primarily focused on the moduli spaces of maximal commutative sub-algebras.
\item Used and developed tools in non-commutative ring theory, category theory, and other related fields.
\end{rSubsection}

\end{rSection}

% \begin{rSection}{Career Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{Lempel-Ziv-Welch Compression Algorithm Implementation}
                   {November 2019}{Written in C}{}
\item Developed specialized Trie Heap data structure to optimize time and space complexity of program under a variety of realistic conditions.
\item Observed improved memory usage and cpu performance over a more traditional Hash Table implementation.

\end{rSubsection}

%\begin{rSubsection}{Object-Oriented Hash Table}
%                   {October 2019}{Written in C}{}
%\item Created reusable Hash Table design which interfaces with user-supplied hash, compare, and destroy functions.
%\item Tested implementation extensively for expected behaviour, as well as for memory leaks and performance issues.
%\end{rSubsection}

{\bf }

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Python, Java, C, Matlab \\
Software \& Tools & Linux, Bash, Git, Valgrind, GDB, Latex  \\
\end{tabular}

\end{rSection}


\newpage
% Academic Achievements
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 

\begin{rSubsection}{Accenture Outstanding Junior Math Award}{June 2020}{Cal Poly Mathematics Department}{}
\item Awarded for demonstrating both superior leadership skills and the ability to work effectively with peers and faculty.
\end{rSubsection}

\begin{rSubsection}{Edward Van Duyne Memorial Scholarship}{June 2019, June 2020}{Cal Poly Mathematics Department}{}
\item Two time recipient of scholarship intended for high-achieving students in the mathematics major.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
%\begin{rSection}{Extra-Curricular} \itemsep -3pt

%\begin{rSubsection}{Cal Poly Math Club Treasurer}{May 2019 - June 2020}{}{}
%\item Tasked with managing club finances, helping coordinate club activities, and overseeing club sales.
%\end{rSubsection}

%\begin{rSubsection}{Polysat Software Team Member}{November 2019 - Present}{}{}
%\item Collaborate with other members to deliver and maintain software for Cal Poly CubeSat missions.
%\end{rSubsection}

%\end{rSection}

\end{document}
